\texttt{davos}: The Python package smuggler

### 2022-04-13 paper/main.tex
author contribution section
add current uses to impact section

% ------------------------------------------------------- IMPACT -------------------------------------------------------
\section{Impact}

@@

>>>>

% ------------------------------------------------------- IMPACT -------------------------------------------------------
\section{Impact}
\comment{
- research domain-independent application
- applicability not limited to research
  - regression (?) testing
- mention something about not having to teach environment management to teach day 1 python lesson, or spend hours debugging conda installation in order to share tutorial or demo with students
}

Despite the short time since its conception and initial release, \texttt{davos} has already found use in a variety of applications. 
In addition to managing data analysis environments for multiple ongoing research studies, \texttt{davos} is being used by both students and instructors in programming courses such as \href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling with Data}} \cite{Mann21b} (an open course on data science, visualization, and communication) to simplify distributing lessons and submitting assignments, as well as in online demos such as {\texttt{abstract2paper}} \cite{Mann21a} (an example application of \href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share ready-to-run code that installs dependencies automatically.

@@

\section*{Author Contributions}
\textbf{Paxton C. Fitzpatrick}: Conceptualization, Methodology, Software, Validation, Writing - Original Draft, Visualization. \textbf{Jeremy R. Manning}: Conceptualization, Resources, Writing - Review \& Editing, Supervision, Funding acquisition.
